### 2020-06-11 writeup/app_exp.tex
sec F

\textbf{Single-task based metric.}
We simplify the setup of this experiment by fixing the sample sizes of every task pair.
For sentiment analysis tasks, the source task uses xx training samples and the target task uses $1000$ training samples for every task pair.
For image classification tasks, the training sample size is 10,000 for every task.

\textbf{Incremental training schedule.}
For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train} below to a round-robin training schedule baseline.
We set the parameters of Algorithm \ref{alg_inc_train} using batch size $32$ and epochs $T = xx$.
The threshold $\tau$ is set as the accuracy of the target task using the baseline training schedule.

For the case of six tasks,

\begin{algorithm}[!h]
	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
		\Output The trained modules $B, W_2$ optimized for task $2$.
		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
		\For{$i = 1,\dots, S$}
			\For{$j = 1,\dots, T$}
				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
			\EndFor
			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
				\State \textbf{break}
			\EndIf
		\EndFor
	\end{algorithmic}
\end{algorithm}

\textbf{Theoretical validation.}
For Figure \ref{fig_ab_sim}, \todo{how do we select each task pair?}
For Figure \ref{fig_ab_data} and Figure \ref{fig_ab_cov}, the sample size of the target task is fixed as $1000$.
We vary the sample size of the source task from $100$ to $3000$.

@@

\textbf{Further results on covariance alignment.}
Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always help.
One possible explanation is overfitting because of additional parameters from the alignment module.
It would be interesting to understand when adding the alignment module provides benefit to the multi-task learning model.
We leave this question for future work.
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
		\label{fig_cov_a}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
			\label{fig_cov_b}
	\end{subfigure}
	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance. We suspect that this happens because of overfitting on the extra parameters in the additional covariance alignment module.}
	\label{fig_covariate_app}
\end{figure}

>>>>

\textbf{Single-task based metric.}
We simplify the setup of this experiment by fixing the sample sizes of every task pair.
For sentiment analysis tasks, the sample size of the source task ranges in $500, 1000, 1500$.
We randomly sample these many data points from the task.
The sample size of the target task is $1000$.
For image classification tasks, the training sample size is $10,000$ for every task.

\textbf{Incremental training schedule.}
For the case of two tasks, we compare the incremental training scheduled described in Algorithm \ref{alg_inc_train} below to a round-robin training schedule baseline.
We add $20\%$ of source task samples for every $T = 2$ epochs.
The total number of epochs is $20$.
We set the threshold $\tau$ as the accuracy of the target task using the baseline training schedule.

For the case of six tasks, we extend Algorithm \ref{alg_inc_train} accordingly.
Initially, we use $5\%$ of samples from SST and $50\%$ of samples from the other tasks.
We add $19\%$ of samples from SST and $5\%$ of samples from the other tasks for every $2$ epochs.
We run $20$ epochs in total.

\begin{algorithm}[!t]
	\caption{An incremental training schedule for efficient multi-task learning with two tasks}
	\label{alg_inc_train}
	\begin{algorithmic}[1]
		\Input Two tasks $(X_1, Y_1)$ and $(X_2, Y_2)$.
		\Param A shared module $B$, output layers $W_1, W_2$ as in the hard parameter sharing architecture.
		\Req \# batches $S$, epochs $T$, task $2$'s validation accuracy $\hat{g}(B; W_2)$, a threshold $\tau\in(0,1)$.
		\Output The trained modules $B, W_2$ optimized for task $2$.
		\State Divide $(X_1, Y_1)$ randomly into $S$ batches: $(x^{(1)}, y^{(1)}), \dots, (x^{(S)}, y^{(S)})$.
		\For{$i = 1,\dots, S$}
			\For{$j = 1,\dots, T$}
				\State Update $B, W_1, W_2$ using the training data $\set{x^{(k)}, x^{(k)}}_{k=1}^i$ and  $(X_2, Y_2)$.
			\EndFor
			\State Let $a_i = \hat{g}(B; W_2)$ be the validation accuracy.
			\If{$a_i < a_{i-1}$ or $a_i > \tau$}
				\State \textbf{break}
			\EndIf
		\EndFor
	\end{algorithmic}
\end{algorithm}

\textbf{Theoretical validation.}
For Figure \ref{fig_ab_sim}, we select a similar and a dissimilar source task compared to the target task using domain knowledge.
First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
TREC is less similar to MR because the task is about question types.
Third pair: MPQA (opinion polarity) is more similar to TREC (question type)

For Figure \ref{fig_ab_data} and Figure \ref{fig_ab_cov}, we fix the sample size of the target task as $1000$.
We vary the sample size of the source task from $100$ to $3000$.
For Figure \ref{fig_ab_cov}, we implement the covariance alignment procedure following \cite{WZR20}.

@@

\textbf{Further results of the covariance alignment procedure.}
Our results in Figure \ref{fig_ab_cov} are averaged over all the task pairs.
In Figure \ref{fig_covariate_app}, we show two task pairs as examples.
In Figure \ref{fig_cov_a}, we observe that for the particular task pair, covariance alignment provides more significant gains when the sample ratio is large.
In Figure \ref{fig_cov_b}, we observe that covariance alignment does not always help.
One explanation is over-fitting because of additional parameters from the alignment module.
An interesting question is to understand when adding the alignment module benefits the multi-task learning model.
We leave this question for future work.
%Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14,

\begin{figure}%[!t]
	\centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
		\label{fig_cov_a}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\includegraphics[width=0.75\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
			\label{fig_cov_b}
	\end{subfigure}
	\caption{(a) For the task pair TREC and CR, adding the covariance alignment procedure provides more improvement when the source/target sample ratio is large.
	(b) For the task pair MR and SST, adding the covariance alignment procedure hurts performance.
	We suspect that this happens because of over-fitting on the extra parameters in the additional covariance alignment module.}
	\label{fig_covariate_app}
\end{figure}

### 2020-06-11 writeup/related.tex
sec F

Our proposed algorithmic consequences also have the potential to help both researchers and practitioners to better develop their multi-task learning applications.
For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult and expensive to acquire large amounts of labeled data.
For such settings, our proposed training scheduler might improve the model training efficiency without requiring huge amounts of labeled data.
For another example, practitioners in industry often need to improve prediction performance by training many related tasks.
But the results are not always positive and practitioners have a hard time figuring out why.
Our proposed metric can provide guidance for selecting which tasks should be trained together in a multi-task model.

>>>>

Our proposed algorithmic consequences also have the potential to help both researchers and practitioners to better develop their use cases of multi-task learning.
For example, many medical applications use multi-task learning to train large-scale image classification models by combining multiple datasets \cite{chexnet17,EA20}.
Unlike the applications of multi-task learning in text classification where large amounts of labeled data are collected \cite{GLUE}, in medical applications it is typically difficult and expensive to acquire large amounts of labeled data.
For such settings, our proposed training scheduler might improve the model training efficiency without requiring huge amounts of labeled data.
For another example, practitioners in industry often need to improve prediction performance by training many related tasks.
But the results are not always positive and practitioners have a hard time figuring out why.
Our proposed metric can provide guidance for selecting which tasks should be trained together in a multi-task model.
